SIR Model With Testing Flows and Isolation

### 2020-12-09 codes/ali_test_sir.Rmd
update

```{r packages, message=FALSE}
library(deSolve)
library(ggplot2)
library(tidyr)
library(McMasterPandemic)
library(directlabels)
library(latex2exp)
library(rootSolve)
unpack <- McMasterPandemic::unpack

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, #0.8, 1/3
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_c=0.01, #isolation parameter 
            s=2 #eta_w/eta_c
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
```

@@

# DFE; analytic approach
Su <- Su_dfe(params)
Sn <- Sn_dfe(params)

state_dfe <- c(S_u=Su, S_n=Sn,
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r model_run, message=FALSE}
out <- as.data.frame(
  ode(
    func=sir.model,
    y=state_init,
    times= d, 
    parms=update(params,beta=2)
    # atol = 1e+1, rtol = 1e+1
    # rootfun = rootfun,
    # method="lsodar"
  )
)

@@

```{r run2, message=FALSE}
d_long <- seq(0,300,by=0.1)
## capturing badly behaved integrator warning messages
cc <- capture.output(
    out_long <- as.data.frame(
        ode(
    func=sir.model,
    y=state_init,
    times= d_long, 
    parms=update(params,beta=2)
    # rootfun = rootfun,
    # method="lsodar"
  )
  ))
out_long2 <- out_long %>%
    pivot_longer(c(S_u,S_n,I_u,I_n,I_p,I_t, R_u,R_n,R_p,R_t),
                 names_to = "compartment", values_to = "value")

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}
F_I <- function(params){
   # Returns F_I at DFE 
  unpack(as.list(params))
  Sn<- Sn_dfe(params)
  Su<- N0-Sn
  sigma <- rho*N0/(W_S*Su) #at DFE 
  return(sigma*W_I)
}

 # just a test
  F_I(params=update(params,rho=0))

R0<-function(params){
    unpack(as.list(params))
    Sn <- Sn_dfe(params)
    Su <- N0-Sn
    # print(c(Su_dfe,Sn_dfe,Su_dfe+Sn_dfe))
    Fi <- F_I(params) #at DFE
    A <-gamma*(omega+gamma+eta_w*Fi) + omega*eta_c*p_I*Fi
    B <-(omega+eta_w*(Fi+gamma))*gamma+(eta_w*gamma+eta_c*omega)*(omega*p_I*Fi)/(omega+gamma)
    C <- beta/(N0*gamma*(gamma*(omega+gamma)+Fi*(gamma+omega*p_I)))
    return((A*Su+B*Sn)*C)
}

# R0 expression with eta_w/eta_c factored
R02<-function(params){
    unpack(as.list(params))
    Sn<- Sn_dfe(params)
    Su<- N0-Sn
    F_I <-F_I(params)  #at DFE

    A2 <- gamma*(p_I*F_I*omega*Sn+(omega+gamma)*(gamma*Sn+F_I*N0))
    B2 <- p_I*F_I*omega*(gamma*Su+omega*N0)
    D <- gamma*(omega+gamma)*(gamma*Su+omega*N0)
    C2 <- beta/((N0*gamma*(gamma*(omega+gamma)+F_I*(gamma+omega*p_I)))*(omega+gamma))
    # s <- eta_w/eta_c
    return((eta_c*(s*A2+B2)+D)*C2)
}

>>>>

```{r packages, message=FALSE}
library(ggplot2)
library(tidyr)
library(directlabels)
library(latex2exp)
library(rootSolve)

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, #0.8, 1/3
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_c=0.01, #isolation parameter 
            s=2 #eta_w/eta_c
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
sim_time <- seq(0,200,by=0.1)
```

@@

# DFE; analytic approach
Su <- Su_dfe(params)
Sn <- Sn_dfe(params)
state_dfe <- c(S_u=Su, S_n=Sn,
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r model_run, message=FALSE}
out <- run.sir(model=sir.model,
               params=update(params,beta=2),
               state=state_init,
               sim_time=sim_time)

@@

```{r run2, message=FALSE}
sim_time_long <- seq(0,300,by=0.1)
## capturing badly behaved integrator warning messages
cc <- capture.output(
   out_long <- run.sir(model=sir.model,
               params=update(params,beta=2),
               state=state_init,
               sim_time=sim_time_long)
)

out_long2 <- out_long %>%
    pivot_longer(c(S_u,S_n,I_u,I_n,I_p,I_t, R_u,R_n,R_p,R_t),
                 names_to = "compartment", values_to = "value")

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.

```{r R0, echo=FALSE}
F_I(state=state_dfe,params=params)
